### 2015-05-19 conclusion.tex
diagrams, implem drivers & OS theory
rfc

\section{Future work}

@@

\paragraph{Registering public key verification with the crypto API}
As we saw in \ref{sec:section-with-RSA-BA414}, the driver is already capable of offloading a large portion of public key operations to the IP, but only with very specific libraries at the time being -- openSSL in our case.
The next step is to register the very same operations with the crypto API so it can be used without having to rely on a custom openSSL engine.
This feature would require to work very closely to the linux kernel developpement.
Indeed, if the signature verification using public key cryptography has been available in the kernel since 2013, a public key encryption API has only been introduced in late April 2015~\cite{cyrpto-api-pk-encryption} and is still under request for comments.

>>>>

\section{Future work}\label{sec:future-work}

@@

\paragraph{Registering public key verification with the crypto API}
As we saw in \ref{sec:section-with-RSA-BA414}, the driver is already capable of offloading a large portion of public key operations to the IP, but only with very specific libraries at the time being -- openSSL in our case.
The next step is to register the very same operations with the crypto API so it can be used without having to rely on a custom openSSL engine.
This feature would require to work very closely to the linux kernel developpement.
Indeed, if the signature verification using public key cryptography has been available in the kernel since 2013, a public key encryption API has only been proposed in late April 2015~\cite{crypto-api-pk-encryption} and is still under request for comments.
